Hydrodynamics of a Semi-Permeable Vesicle Under Flow and Confinement???

### 2020-12-14 vesicle_code/docs/permeableVes/main.tex
working on contracting images
updated title

\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
Physics}

@@

>>>>

%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
%Physics}
\title{Hydrodynamics of a Semi-Permeable Vesicle Under Flow and
Confinement???}

@@

\begin{figure*}[htp]
  \centering
%  \ifTikz
  \input{figures/contractingComposite.tikz}
%  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, and
  the vesicle height is initially $10\mu$m.}
\end{figure*}
